\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{fontawesome5}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\IfFileExists{glyphtounicode.tex}{\input{glyphtounicode}}{}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-2pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}, itemsep=2.5pt, parsep=0pt, topsep=1.5pt, partopsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, itemsep=1.5pt, parsep=0pt, topsep=1.5pt, partopsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Arekanti Siddartha} \\ \vspace{2pt}
    \href{https://github.com/Siddartharekanti}{\raisebox{0\height}\faGithub\ {Github}}
    ~ $|$ ~ 
    \href{https://www.linkedin.com/in/siddartha-arekanti-05557b24b/}{\raisebox{0\height}\faLinkedin\ {Linkedin}}
    ~ $|$ ~ 
    \href{https://leetcode.com/u/Siddartha_A/}{\raisebox{0\height}\faCode\ {LeetCode}}
    ~ $|$ ~ 
    \href{mailto:siddarthaarekanti@gmail.com}{\raisebox{-0.1\height}\faEnvelope\  {siddarthaarekanti@gmail.com}}
    ~ $|$ ~ 
    \small \raisebox{-0.01\height}\faPhone\ +91 8688050497
    \vspace{-12pt}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SRM University}{Amaravati, Andhra Pradesh}
      {M.Tech in Cyber Security; \textbf{CGPA: 8.30/10.0}}{Sep 2025 -- Jun 2027 (Expected)}
    \resumeSubheading
      {SRM University}{Amaravati, Andhra Pradesh}
      {B.Tech in Computer Science and Engineering; \textbf{CGPA: 7.57/10.0}}{Jun 2021 -- May 2025}
  \resumeSubHeadingListEnd
\vspace{-14pt}

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineering Intern}{May 2024 -- Jul 2024}
      {SECENAI Semiconductors and Test Solutions Pvt. Ltd.}{Amaravati, Andhra Pradesh}
      \resumeItemListStart
        \resumeItem{Architected a Student Attendance System using Face Recognition and OpenCV with 95\%+ identification accuracy for 100+ students.}
        \resumeItem{Automated attendance tracking with Machine Learning algorithms including SVM and CNN, improving efficiency by 80\% versus manual methods.}
        \resumeItem{Engineered real-time facial detection and recognition pipeline using Python, OpenCV, NumPy, and scikit-learn.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-14pt}

\section{Patents \& Publications}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{FEELGAN: Federated Edge Learning with GANs for Medical Image Analysis}}{}
        \resumeItemListStart
            \resumeItem{Patent Approved (Application No: 202441083307) -- Pioneered a privacy-preserving disease detection system using federated learning, generative adversarial networks, and decentralized healthcare diagnostics.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-14pt}

\section{Projects}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{FEELGAN - Medical Image Analysis System} $|$ \emph{Python, TensorFlow, PyTorch, GANs, CNNs, Federated Learning}}{}
          \resumeItemListStart
            \resumeItem{Developed FEELGAN - Medical Image Analysis System using Python, TensorFlow, PyTorch, GANs, CNNs, Federated Learning, aligned with Python, Tensorflow, Pytorch, CNNs, Image Analysis.}
            \resumeItem{Implemented Synthetic medical image generation, CNN classification, COVID-19/TB/OCT dataset training, federated learning workflow, improving practical coverage of production-style workflows.}
            \resumeItem{Delivered measurable outcomes including 15\% diagnostic accuracy improvement, 10,000+ synthetic medical images, 90\%+ accuracy.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{AI-Powered Documentation ChatBot} $|$ \emph{Python, React, FastAPI, RAG, LLM, OpenAI, Embeddings}}{}
          \resumeItemListStart
            \resumeItem{Developed AI-Powered Documentation ChatBot using Python, React, FastAPI, RAG, LLM, OpenAI, aligned with Python, Fastapi, REST API, API, Rag.}
            \resumeItem{Implemented Document parsing, cleaning, chunking, semantic search, improving practical coverage of production-style workflows.}
            \resumeItem{Delivered measurable outcomes including 1,000+ pages processed, sub-second response times.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Student Attendance System} $|$ \emph{Python, OpenCV, NumPy, scikit-learn, SVM, CNN}}{}
          \resumeItemListStart
            \resumeItem{Developed Student Attendance System using Python, OpenCV, NumPy, scikit-learn, SVM, CNN, aligned with Python, Model.}
            \resumeItem{Implemented Face detection, face recognition, attendance logging, model training, improving practical coverage of production-style workflows.}
            \resumeItem{Delivered measurable outcomes including 95\%+ identification accuracy, 100+ students.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-14pt}

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt, parsep=0pt, topsep=0pt]
    \small{\item{
     \textbf{Languages}{: Python, C++, HTML/CSS, JavaScript, SQL} \\
     \textbf{Frameworks \& Libraries}{: PyTorch, TensorFlow, Flask, Node.js, OpenCV, React, scikit-learn} \\
     \textbf{Databases}{: MongoDB, MySQL} \\
     \textbf{Developer Tools}{: Docker, Git, GitHub, Jupyter Notebook, Postman, PyCharm, VS Code} \\
     \textbf{Core Competencies}{: CNNs, Computer Vision, Deep Learning, Federated Learning, Machine Learning, REST APIs, GANs} \\
    }}
 \end{itemize}
 \vspace{-16pt}

\section{Certifications}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{Deep Learning with PyTorch} -- Udemy}{2024}
        \resumeProjectHeading
            {\textbf{Machine Learning Specialization} -- Coursera}{2024}
        \resumeProjectHeading
            {\textbf{Full Stack Web Development} -- freeCodeCamp}{2023}
    \resumeSubHeadingListEnd
\vspace{-14pt}

\section{Achievements}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{LeetCode} -- Solved 350+ problems across data structures and algorithms}{}
        \resumeProjectHeading
            {\textbf{Anveshan 2024} -- Presented FEELGAN at National Student Research Program}{}
        \resumeProjectHeading
            {\textbf{Sushacks 2025} -- Competed in Nationwide Innovation Hackathon}{}
    \resumeSubHeadingListEnd

\end{document}
